% =========================================================================
% §0 Abstract
% Budget: ~0.4 pp (single paragraph)
% Drafting order: LAST (after Introduction is in shape).
%
% Content blueprint (RESEARCH_paper_outline.md §4 / Abstract):
%   - Empirical question (does a structural codebase index in a fixed
%     coding-agent harness change cost or resolve, controlled for model?)
%   - Design (1 model held fixed: Opus 4.7; 3 arms: SC-ON / SC-OFF / OpenCode;
%     SWE-PolyBench Verified + SWE-bench-Pro; leak-audited; paired n=75)
%   - Headline numbers (multi-seed): View B acc@5 ablation +39.6 pp paired,
%     p<0.0001; resolve ablation +7.9 pp paired, p=0.003; per-cell cost
%     statistically null. [Updated 2026-06-17 after multi-seed rewrite.]
%   - Cross-harness: matches OpenCode on resolve and View B acc@5 at no
%     cost penalty (qualitative; no explicit numbers in abstract).
%   - Released artifacts: ledger, leak-audit script, dual-view extractor,
%     results DB.
%
% Constraints:
%   - Cost is supporting evidence, not the headline.
%   - No marketing voice.
%   - Multi-seed posture (three seeds); abstract carries no seed-variance
%     discussion. Seed scope stated once in the design sentence.
%   - No honest negatives in abstract (live in Results + Discussion).
%   - No citations, no cross-refs.
% =========================================================================

\begin{abstract}
Coding agents now interleave LLMs with retrieval over the working repository, and
retrieval implementations vary widely across deployed harnesses. Inside a fixed
coding-agent harness on a fixed model, does adding a structural codebase index actually
change cost or resolve? We ran three arms (the harness with the index, the same harness
without it, and an agentic-grep comparator) on SWE-PolyBench Verified and SWE-bench Pro
with Claude Opus~4.7 \citep{claudeopus47} held fixed throughout, across three seeds, inside a leak-audited
per-task sandbox. The within-harness ablation produces a large localization
gain and a statistically separated resolve gain, with no cost penalty per cell and lower
cost per solve. The cross-harness check shows that the index does not regress against an
agentic-grep baseline on resolve or localization, again at no cost penalty. We release
the per-cell exclusion ledger, the leak-audit script, the localization extractor, and the
results database. The deployment question for a structural codebase index is thus not
whether it is too expensive to run (across seeds, the index lands at a lower \$/solved
than agentic grep) but whether the workload includes multi-file changes where structural
ranking pays off.
\end{abstract}

\vspace{0.3em}
\noindent\textbf{Keywords:} coding agents, code retrieval, structural codebase index,
causal ablation, SWE-bench.
