% =========================================================================
% §5 Integrity & Threats to Validity
% Budget: ~1.0 pp
% Drafting order: Right after Experimental Design.
% Genre precedent: Agentless §7 + SpecRover V-A "Data Memorization".
%
% Content blueprint:
%   - 5.1 Pre-run hardening: URL redaction; per-cell git scrub
%     (refs -> physical prune); fail-closed gate (scrub=DIRTY aborts).
%   - 5.2 Post-run audit (S1 reviewer pass): re-ran leak_audit.py over
%     386 archived traces. Found 5 additional git_history_leak cells
%     (past-commit `git show` of a gold-file diff). Excluded outcome-blind.
%     Per-arm: SC-ON 1, SC-OFF 2, OpenCode 2. Two had resolved=1.
%     Corrects an earlier "SC-ON never leaked" belief. Network-fetch audit
%     re-run and clean.
%   - 5.3 Exclusion taxonomy: 26 cells across 8 categories. Per-arm:
%     SC-ON 7, SC-OFF 9, OpenCode 10. scrub_failed whole-instance balanced
%     (4/4/4).
%   - 5.4 Public ledger: released exclusion_ledger.csv (cell_id,
%     instance_id, harness, arm, exclusion_reason, evidence; e.g.
%     `git show <hash> -> <gold file>`).
%   - 5.5 Threats: n=75 paired limit; 3-of-5 language coverage (no
%     JS/TS); in-ancestry leak residual; provider-truncation asymmetry
%     (5/5 on SC arms, 0 on OpenCode; excluded so doesn't bias rates);
%     localization extractor sensitivity (dual-view reported).
%
% Tables (under tables/):
%   - tab-exclusion-taxonomy.tex: 5 cols (Category, SC-ON, SC-OFF,
%     OpenCode, Total) over 5 rows + totals.
%
% Constraints:
%   - Public ledger is foregrounded as a credibility artifact.
%   - The S1 finding that SC-ON also leaked once is stated plainly.
% =========================================================================

\section{Integrity and Threats to Validity}
\label{sec:integrity}

The integrity load for this study sits in four places: pre-run hardening of the per-cell
sandbox, a post-run audit that re-checked every kept cell for residual leakage, the
exclusion taxonomy that explains which cells were dropped and why, and a named threats list
that points the reader at the residual concerns the audit could not eliminate. The
released artifacts that back this section are \texttt{data/exclusion\_ledger.csv} (the
exclusion ledger), \texttt{scoring/leak\_audit.py} (the auditor), and
\texttt{scoring/localization.py} (the localization extractor that emits both views).

\subsection{Pre-run hardening}
\label{sec:integrity-hardening}

Two mechanisms ran before every cell. \textbf{URL redaction.} Self-links in problem
statements were stripped at spec-build time, so the agent could not navigate to a
canonical-fix page through the prompt. \textbf{Git scrub.} Every cell starts from a
sandbox whose repo has the gold-fix commit and its descendants stripped. Refs deletion
alone is not sufficient: \texttt{git show <hash>} still recovers any object reachable in
the object database, so the hardened path runs \texttt{git gc --prune=now} to physically
remove the dropped objects. A post-scrub object-set check then verifies that no
future-commit objects remain reachable; if any do, the cell is marked
\texttt{scrub=DIRTY} and aborted before the agent runs. Only \texttt{scrub=CLEAN} cells
execute. In the released set, 12 cells tripped this fail-closed gate and appear in the
ledger as \texttt{scrub\_failed}; the trip is whole-instance and arm-independent, so the
distribution is balanced across the three arms (Table~\ref{tab:exclusion-taxonomy}).

\subsection{Post-run audit}
\label{sec:integrity-audit}

After the run completed we re-executed \texttt{leak\_audit.py} over 386 archived
traces from the released set as an S1 reviewer pass. The audit found 5 additional
\texttt{git\_history\_leak} cells: the agent had invoked \texttt{git show <historical-hash>}
on a past commit whose diff touches a gold file. These are commits in the base history
that pre-date the scrub window; the scrub cannot remove them without changing the task
specification. The 5 cells were excluded outcome-blind (any arm, any outcome); the
per-arm breakdown and which were resolved=1 appear in the ledger
(Table~\ref{tab:exclusion-taxonomy}, and \texttt{data/exclusion\_ledger.csv}). Post-exclusion,
the residual impact on every reported metric is under 1\,pp, and no metric ordering flips;
the triple-intersection paired-$n$ moved from 79 to 75. A network-fetch audit was re-run on
the same 386 traces and came back clean (no kept cell fetched a high-severity hosting URL).
The in-ancestry class itself (gold fix reachable in base history) is a dataset limitation
that detect-and-exclude can shrink but not eliminate; the sub-1\,pp figure is what survives
in the released set.

\subsection{Exclusion taxonomy and public ledger}
\label{sec:integrity-ledger}

Twenty-six cells were excluded across the five categories that appear in the public
ledger (Table~\ref{tab:exclusion-taxonomy}). Every excluded cell is removed before
resolve, cost, and localization rates are computed; only legit cells enter denominators
(\S\ref{sec:design-metrics}). Three balance points are worth surfacing.
\texttt{scrub\_failed} is whole-instance balanced across arms, which is the posture the
fail-closed gate is designed to produce. \texttt{provider\_truncation} is arm-asymmetric:
all 5 exclusions land on SuperCoder arms, flagged again in \S\ref{sec:integrity-threats}.
\texttt{git\_history\_leak} (flagged above) and \texttt{leak\_detected} (OpenCode only)
round out the ledger; per-arm counts for every category appear in
Table~\ref{tab:exclusion-taxonomy}. The public artifact
\texttt{data/exclusion\_ledger.csv} carries one row per excluded cell with columns
\texttt{cell\_id}, \texttt{instance\_id}, \texttt{harness}, \texttt{arm},
\texttt{exclusion\_reason}, and \texttt{evidence}; the \texttt{evidence} column quotes
the concrete trigger (for \texttt{git\_history\_leak} rows, the literal
\texttt{git show <hash>} invocation against the gold file). The ledger has been through a
three-check audit pass: structural (every excluded \texttt{cell\_id} resolves in the main
DB), forensic (each \texttt{git\_history\_leak} row hand-confirmed against its trace),
and gold-set verification (every \texttt{instance\_id}'s gold file set matches the
benchmark specification).

\begin{table}[!tbp]
  \centering
  \caption{Exclusion taxonomy. Counts recomputed from
    \texttt{data/exclusion\_ledger.csv}; row totals sum to 26 across 5 categories. All
    excluded cells are removed from rate denominators.}
  \label{tab:exclusion-taxonomy}
  \input{tables/tab-exclusion-taxonomy}
\end{table}

\FloatBarrier
\subsection{Threats to validity}
\label{sec:integrity-threats}

Six residual threats survive the hardening and the audit. \textbf{Paired-$n$ limits.}
Effective denominators are 75 (triple-intersection), 80 (SC-ON vs.\ SC-OFF), and 78
(SC-ON vs.\ OpenCode), defined in \S\ref{sec:design-scope}; resolve-level paired tests
are under-powered at these sizes, and \S\ref{sec:results} states that limitation at every
test. \textbf{Language coverage.} Three of the five SWE-PolyBench languages are
represented (Go, Java, Python); JavaScript and TypeScript were not run, so
generalization beyond these three is not warranted.
\textbf{\texttt{provider\_truncation} asymmetry.} All 5 truncation exclusions fall on the
SuperCoder arms (none on OpenCode); per-arm counts are in
Table~\ref{tab:exclusion-taxonomy}. Because the cells are excluded rather than scored,
the asymmetry does not directly bias the reported rates, but what was lost differs across
arms and is worth flagging. \textbf{Localization extractor sensitivity.} The metric
admits two defensible computations; we report both views throughout
(\S\ref{sec:design-localization}, \S\ref{sec:results}), and the dual-view disclosure is
the mitigation. \textbf{In-ancestry leak residual.} Where the gold fix is reachable in
base history, the scrub cannot remove it without altering the task; detect-and-exclude
(\S\ref{sec:integrity-audit}) shrinks but cannot eliminate this class.
\textbf{Issue-text phrasing realism.} We feed the agent the formal GitHub-issue text from
the upstream benchmarks; \citet{savingswebench2025} show that mutating issue text into
realistic chat-style queries derived from agent telemetry can drop measured pass rates by
over 50\% on some models, an ecological-validity gap that detect-and-exclude does not
address. The reported absolute resolve rates should be read as benchmark-conditional;
the within-harness ablation is robust to this gap because both arms see identical text.
